---
title: "How many colours are in each national flag?"
author: "Tejas Kale"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: paper
    df_print: paged
---

Wikipedia publishes a [list of sovereign states](https://en.wikipedia.org/wiki/List_of_sovereign_states)
together with each country's flag. This notebook scrapes that list, downloads a
PNG thumbnail of every flag, then asks three vision models on
[OpenRouter](https://openrouter.ai) to look at the pictures:

1. **Google Gemini 3.5 Flash Lite** (`google/gemini-3.5-flash-lite`) counts the
   distinct colours and names them, via the [ellmer](https://ellmer.tidyverse.org)
   `chat_openrouter()` client.
2. **Qwen3-VL-235B-A22B Instruct** (`qwen/qwen3-vl-235b-a22b-instruct`), the
   flagship vision model from Alibaba's Qwen team, looks at the same flag and
   judges Gemini's answer.
3. **Google Gemini 3.6 Flash** (`google/gemini-3.6-flash`) runs the same judge
   prompt independently, so we can compare two referees against the cheap
   counter.

Set `OPENROUTER_API_KEY` in the environment (or in `~/.Renviron`) before knitting
the model chunks. Wikipedia scraping and flag downloads run without a key.

Optional knobs:

- `MAX_FLAGS` — process only the first *n* countries (useful while testing).
- `FLAG_COLOUR_CACHE` — path to an RDS cache so a interrupted run can resume.

This notebook was generated with [Cursor](https://cursor.com). I reviewed and
modified the code.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r packages}
library(rvest)
library(httr2)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(ellmer)
library(gt)
library(ggplot2)
library(scales)
```

## 1. Countries from Wikipedia

The first sortable table on *List of sovereign states* is the usual census of
UN members and observer states (about 195 rows). Each country cell starts with a
`flagicon` thumbnail and a bold link. Letter-index header rows are skipped
because they have no flag.

```{r wikipedia-countries}
wiki_url <- "https://en.wikipedia.org/wiki/List_of_sovereign_states"
ua <- "FlagColourNotebook/1.0 (https://tejas-kale.github.io/blog/; educational flag-colour analysis)"

wiki_html <- request(wiki_url) |>
  req_user_agent(ua) |>
  req_perform() |>
  resp_body_html()

country_rows <- wiki_html |>
  html_element("table.wikitable.sortable") |>
  html_elements("tr")

countries <- map_dfr(country_rows, function(row) {
  cell <- html_element(row, "td")
  if (inherits(cell, "xml_missing") || length(cell) == 0) {
    return(NULL)
  }
  flag_img <- html_element(cell, "span.flagicon img")
  name_link <- html_element(cell, "span.flagicon + a")
  if (inherits(name_link, "xml_missing") || length(name_link) == 0) {
    name_link <- html_element(cell, "b a[href*='/wiki/']")
  }
  if (inherits(flag_img, "xml_missing") || length(flag_img) == 0 ||
      inherits(name_link, "xml_missing") || length(name_link) == 0) {
    return(NULL)
  }
  tibble(
    country = html_text2(name_link),
    wiki_href = html_attr(name_link, "href"),
    thumb_src = html_attr(flag_img, "src")
  )
}) |>
  filter(!is.na(country), country != "") |>
  mutate(
    wiki_url = xml2::url_absolute(wiki_href, "https://en.wikipedia.org/"),
    # Standard thumbnail steps only (20, 40, 60, 120, 250, …); 200px is 400.
    thumb_url = if_else(
      str_starts(thumb_src, "//"),
      paste0("https:", thumb_src),
      thumb_src
    ) |>
      str_replace("/\\d+px-", "/250px-") |>
      str_replace("\\?.*$", "")
  ) |>
  distinct(country, .keep_all = TRUE)

max_flags <- suppressWarnings(as.integer(Sys.getenv("MAX_FLAGS", unset = "")))
if (!is.na(max_flags) && max_flags > 0L) {
  countries <- slice_head(countries, n = max_flags)
}

countries
```

## 2. Flag images from Wikipedia

The list already carries Wikimedia thumbnail URLs (PNG renderings of the SVG
flags). Those PNGs are what vision APIs accept. Files are stored under
`/tmp/flag-colours/` so they never land in the repo.

```{r download-flags}
flag_dir <- file.path("/tmp", "flag-colours")
dir.create(flag_dir, recursive = TRUE, showWarnings = FALSE)

slugify <- function(x) {
  x |>
    str_to_lower() |>
    str_replace_all("[^a-z0-9]+", "-") |>
    str_replace_all("(^-+|-+$)", "")
}

countries <- countries |>
  mutate(
    flag_file = file.path(flag_dir, paste0(slugify(country), ".png"))
  )

download_flag <- function(url, dest) {
  if (file.exists(dest) && file.info(dest)$size > 0) {
    return(invisible(dest))
  }
  request(url) |>
    req_user_agent(ua) |>
    req_retry(max_tries = 4) |>
    req_timeout(30) |>
    req_perform(path = dest)
  Sys.sleep(0.1)
  invisible(dest)
}

walk2(countries$thumb_url, countries$flag_file, download_flag)

countries <- countries |>
  mutate(flag_ok = file.exists(flag_file) & file.info(flag_file)$size > 0)

stopifnot(all(countries$flag_ok))
n_countries <- nrow(countries)
```

## 3. Gemini Flash Lite counts the colours

Each flag is sent as an image with a structured schema so Gemini has to return
an integer count and a list of colour names, not free-form prose. A **new**
chat is opened per flag so previous images do not pile up in the context
window. Results are cached after every country.

```{r gemini-colours}
api_key <- Sys.getenv("OPENROUTER_API_KEY")
if (!nzchar(api_key)) {
  knitr::knit_exit(
    "Set OPENROUTER_API_KEY to count colours with Gemini and to run the judges."
  )
}

gemini_model <- "google/gemini-3.5-flash-lite"
judge_model <- "qwen/qwen3-vl-235b-a22b-instruct"
flash_model <- "google/gemini-3.6-flash"

cache_path <- Sys.getenv("FLAG_COLOUR_CACHE", unset = "")
if (!nzchar(cache_path)) {
  candidates <- c(
    file.path("data", "flag_colour_cache.rds"),
    file.path("..", "data", "flag_colour_cache.rds")
  )
  existing <- candidates[file.exists(candidates)]
  cache_path <- if (length(existing) > 0) {
    normalizePath(existing[[1]])
  } else if (basename(getwd()) == "notebooks") {
    file.path("..", "data", "flag_colour_cache.rds")
  } else {
    file.path("data", "flag_colour_cache.rds")
  }
}
dir.create(dirname(cache_path), recursive = TRUE, showWarnings = FALSE)

empty_cache <- tibble(
  country = character(),
  flag_file = character(),
  gemini_n_colours = integer(),
  gemini_colours = character(),
  judge_verdict = character(),
  judge_n_colours = integer(),
  judge_missing = character(),
  judge_extra = character(),
  judge_comments = character(),
  judge_model_used = character(),
  flash_verdict = character(),
  flash_n_colours = integer(),
  flash_missing = character(),
  flash_extra = character(),
  flash_comments = character(),
  flash_model_used = character()
)
cache <- empty_cache
if (file.exists(cache_path)) {
  cache <- bind_rows(empty_cache, readRDS(cache_path)) |>
    distinct(country, .keep_all = TRUE) |>
    mutate(
      judge_verdict = if_else(
        coalesce(judge_model_used, "") == judge_model, judge_verdict, NA_character_
      ),
      judge_n_colours = if_else(
        coalesce(judge_model_used, "") == judge_model, judge_n_colours, NA_integer_
      ),
      judge_missing = if_else(
        coalesce(judge_model_used, "") == judge_model, judge_missing, NA_character_
      ),
      judge_extra = if_else(
        coalesce(judge_model_used, "") == judge_model, judge_extra, NA_character_
      ),
      judge_comments = if_else(
        coalesce(judge_model_used, "") == judge_model, judge_comments, NA_character_
      ),
      flash_verdict = if_else(
        coalesce(flash_model_used, "") == flash_model, flash_verdict, NA_character_
      ),
      flash_n_colours = if_else(
        coalesce(flash_model_used, "") == flash_model, flash_n_colours, NA_integer_
      ),
      flash_missing = if_else(
        coalesce(flash_model_used, "") == flash_model, flash_missing, NA_character_
      ),
      flash_extra = if_else(
        coalesce(flash_model_used, "") == flash_model, flash_extra, NA_character_
      ),
      flash_comments = if_else(
        coalesce(flash_model_used, "") == flash_model, flash_comments, NA_character_
      )
    )
}

flag_type <- type_object(
  n_colours = type_integer(
    "Number of distinct colours that a person would name when describing the flag. Ignore anti-aliasing, shadows, and tiny fimbriations that are only a drawing artefact."
  ),
  colours = type_array(
    type_string(),
    "Common English colour names (for example red, white, navy blue, gold, green). List each colour once, from largest area to smallest."
  )
)

judge_type <- type_object(
  verdict = type_enum(
    c("agree", "mostly_agree", "disagree"),
    "agree = count and names are right; mostly_agree = right idea with a naming or minor-count slip; disagree = a colour is missing, invented, or the count is wrong."
  ),
  correct_n_colours = type_integer(
    "The number of distinct colours you would count on this flag."
  ),
  missing_colours = type_array(
    type_string(),
    "Colours present on the flag that Gemini omitted. Empty if none."
  ),
  extra_colours = type_array(
    type_string(),
    "Colours Gemini named that are not really on the flag. Empty if none."
  ),
  comments = type_string("One or two sentences explaining the verdict.")
)

new_openrouter_chat <- function(model, system_prompt) {
  chat_openrouter(
    system_prompt = system_prompt,
    model = model,
    echo = "none"
  )
}

structured_with_retry <- function(chat_factory, ..., type, tries = 4) {
  last_err <- NULL
  for (i in seq_len(tries)) {
    out <- tryCatch(
      chat_factory()$chat_structured(..., type = type),
      error = function(e) e
    )
    if (!inherits(out, "error")) {
      return(out)
    }
    last_err <- out
    Sys.sleep(min(2^i, 16))
  }
  stop(last_err)
}

gemini_system <- paste(
  "You are looking at a national flag image.",
  "Count the distinct colours a vexillologist would list in a short description.",
  "Treat metal tints such as gold and yellow as the colour you actually see.",
  "Do not invent colours that are not visible."
)

judge_system <- paste(
  "You are a careful second reader of national flags.",
  "You will see the flag image and Gemini's colour list.",
  "Judge whether that list matches the image. Be strict about missing or invented colours,",
  "but treat near-synonyms (navy / dark blue, gold / yellow) as mostly agreeing."
)

collapse_colours <- function(x) {
  if (is.null(x) || length(x) == 0 || all(is.na(x))) {
    return("")
  }
  paste(x, collapse = ", ")
}

pending <- countries |>
  anti_join(
    cache |> filter(!is.na(gemini_n_colours)),
    by = "country"
  )

if (nrow(pending) > 0) {
  message("Gemini: ", nrow(pending), " flags still to score.")
}

for (i in seq_len(nrow(pending))) {
  row <- pending[i, ]
  gemini <- structured_with_retry(
    function() new_openrouter_chat(gemini_model, gemini_system),
    paste0(
      "How many distinct colours are in the flag of ",
      row$country,
      "? Name them."
    ),
    content_image_file(row$flag_file, resize = "low"),
    type = flag_type
  )
  new_row <- tibble(
    country = row$country,
    flag_file = row$flag_file,
    gemini_n_colours = gemini$n_colours,
    gemini_colours = collapse_colours(gemini$colours),
    judge_verdict = NA_character_,
    judge_n_colours = NA_integer_,
    judge_missing = NA_character_,
    judge_extra = NA_character_,
    judge_comments = NA_character_,
    judge_model_used = NA_character_,
    flash_verdict = NA_character_,
    flash_n_colours = NA_integer_,
    flash_missing = NA_character_,
    flash_extra = NA_character_,
    flash_comments = NA_character_,
    flash_model_used = NA_character_
  )
  cache <- bind_rows(filter(cache, country != row$country), new_row)
  saveRDS(cache, cache_path)
}

cache
```

## 4. Qwen3-VL-235B judges Gemini

Qwen3-VL-235B-A22B Instruct is a Mixture-of-Experts vision model from Alibaba /
Qwen (22B active parameters, 235B total). That is a step up from Gemini 3.5
Flash Lite, which is the point of the second pass: the cheaper model proposes
colours, the stronger Chinese-lab model audits them. It sees the flag **and**
Gemini's named list, then returns a verdict, its own count, and a short comment.

```{r qwen-judge}
needs_judge <- cache |>
  filter(is.na(judge_verdict) | judge_verdict == "") |>
  select(-flag_file) |>
  inner_join(countries |> select(country, flag_file), by = "country")

if (nrow(needs_judge) > 0) {
  message("Qwen judge: ", nrow(needs_judge), " flags still to score.")
}

for (i in seq_len(nrow(needs_judge))) {
  row <- needs_judge[i, ]
  judgement <- structured_with_retry(
    function() new_openrouter_chat(judge_model, judge_system),
    paste0(
      "Country: ", row$country, "\n",
      "Gemini said there are ", row$gemini_n_colours,
      " colours: ", row$gemini_colours, "\n",
      "Look at the flag image and judge that answer."
    ),
    content_image_file(row$flag_file, resize = "low"),
    type = judge_type
  )
  cache <- cache |>
    mutate(
      judge_verdict = if_else(
        country == row$country, as.character(judgement$verdict), judge_verdict
      ),
      judge_n_colours = if_else(
        country == row$country, as.integer(judgement$correct_n_colours), judge_n_colours
      ),
      judge_missing = if_else(
        country == row$country, collapse_colours(judgement$missing_colours), judge_missing
      ),
      judge_extra = if_else(
        country == row$country, collapse_colours(judgement$extra_colours), judge_extra
      ),
      judge_comments = if_else(
        country == row$country, judgement$comments, judge_comments
      ),
      judge_model_used = if_else(
        country == row$country, judge_model, judge_model_used
      )
    )
  saveRDS(cache, cache_path)
}
```

## 5. Gemini 3.6 Flash judges Gemini

Gemini 3.6 Flash is the current Flash-tier workhorse from Google: stronger than
3.5 Flash Lite, cheaper and faster than Qwen 235B. It gets the same judge
prompt and schema as Qwen — the flag image plus Gemini Lite's named list — so
the two verdicts are comparable.

```{r gemini-36-judge}
needs_flash <- cache |>
  filter(is.na(flash_verdict) | flash_verdict == "") |>
  select(-flag_file) |>
  inner_join(countries |> select(country, flag_file), by = "country")

if (nrow(needs_flash) > 0) {
  message("Gemini 3.6 Flash judge: ", nrow(needs_flash), " flags still to score.")
}

for (i in seq_len(nrow(needs_flash))) {
  row <- needs_flash[i, ]
  judgement <- structured_with_retry(
    function() new_openrouter_chat(flash_model, judge_system),
    paste0(
      "Country: ", row$country, "\n",
      "Gemini said there are ", row$gemini_n_colours,
      " colours: ", row$gemini_colours, "\n",
      "Look at the flag image and judge that answer."
    ),
    content_image_file(row$flag_file, resize = "low"),
    type = judge_type
  )
  cache <- cache |>
    mutate(
      flash_verdict = if_else(
        country == row$country, as.character(judgement$verdict), flash_verdict
      ),
      flash_n_colours = if_else(
        country == row$country, as.integer(judgement$correct_n_colours), flash_n_colours
      ),
      flash_missing = if_else(
        country == row$country, collapse_colours(judgement$missing_colours), flash_missing
      ),
      flash_extra = if_else(
        country == row$country, collapse_colours(judgement$extra_colours), flash_extra
      ),
      flash_comments = if_else(
        country == row$country, judgement$comments, flash_comments
      ),
      flash_model_used = if_else(
        country == row$country, flash_model, flash_model_used
      )
    )
  saveRDS(cache, cache_path)
  if (i %% 10L == 0L || i == nrow(needs_flash)) {
    message("Gemini 3.6 Flash judge: ", i, "/", nrow(needs_flash))
  }
}
```

## 6. Results

```{r results-table}
results <- countries |>
  select(country, flag_file) |>
  inner_join(cache |> select(-flag_file), by = "country") |>
  arrange(country)

qwen_agree_rate <- mean(results$judge_verdict == "agree", na.rm = TRUE)
flash_agree_rate <- mean(results$flash_verdict == "agree", na.rm = TRUE)

results |>
  select(country, judge_verdict, flash_verdict) |>
  pivot_longer(
    cols = c(judge_verdict, flash_verdict),
    names_to = "judge",
    values_to = "verdict"
  ) |>
  mutate(
    judge = recode(
      judge,
      judge_verdict = "Qwen3-VL-235B",
      flash_verdict = "Gemini 3.6 Flash"
    )
  ) |>
  count(judge, verdict, name = "flags") |>
  group_by(judge) |>
  mutate(share = flags / sum(flags)) |>
  ungroup()
```

Qwen agreed with Gemini Lite on
**`r sprintf("%.0f%%", 100 * qwen_agree_rate)`** of the
`r nrow(results)` flags; Gemini 3.6 Flash agreed on
**`r sprintf("%.0f%%", 100 * flash_agree_rate)`**.

```{r flag-table}
results |>
  select(
    flag_file, country,
    gemini_n_colours, gemini_colours,
    judge_verdict, judge_n_colours,
    judge_missing, judge_extra, judge_comments,
    flash_verdict, flash_n_colours,
    flash_missing, flash_extra, flash_comments
  ) |>
  gt() |>
  text_transform(
    locations = cells_body(columns = flag_file),
    fn = function(x) {
      vapply(x, function(path) {
        img <- as.character(local_image(filename = path, height = 28))
        sub(
          "<img ",
          '<img class="flag-thumb" tabindex="0" title="Click to enlarge" onclick="this.classList.toggle(\'is-zoomed\')" onkeydown="if(event.key===\'Enter\'||event.key===\' \'){event.preventDefault();this.classList.toggle(\'is-zoomed\')}" ',
          img,
          fixed = TRUE
        )
      }, character(1))
    }
  ) |>
  opt_css(
    css = "
    .flag-thumb { cursor: zoom-in; vertical-align: middle; }
    .flag-thumb.is-zoomed { height: 120px !important; width: auto !important; cursor: zoom-out; }
    "
  ) |>
  cols_label(
    flag_file = "",
    country = "Country",
    gemini_n_colours = "Gemini n",
    gemini_colours = "Gemini colours",
    judge_verdict = "Qwen verdict",
    judge_n_colours = "Qwen n",
    judge_missing = "Qwen missing",
    judge_extra = "Qwen extra",
    judge_comments = "Qwen comments",
    flash_verdict = "3.6 Flash verdict",
    flash_n_colours = "3.6 Flash n",
    flash_missing = "3.6 Flash missing",
    flash_extra = "3.6 Flash extra",
    flash_comments = "3.6 Flash comments"
  ) |>
  tab_header(
    title = "National flag colours, according to Gemini 3.5 Flash Lite",
    subtitle = paste(
      "Judged by Qwen3-VL-235B-A22B Instruct and Gemini 3.6 Flash via OpenRouter.",
      "Flags from Wikipedia / Wikimedia Commons."
    )
  ) |>
  tab_source_note(
    "Sources: https://en.wikipedia.org/wiki/List_of_sovereign_states and Wikimedia Commons flag files."
  ) |>
  data_color(
    columns = c(judge_verdict, flash_verdict),
    fn = scales::col_factor(
      palette = c(agree = "#C8E6C9", mostly_agree = "#FFE082", disagree = "#FFCDD2"),
      domain = c("agree", "mostly_agree", "disagree"),
      na.color = "#EEEEEE"
    )
  ) |>
  tab_options(
    table.font.size = px(13),
    data_row.padding = px(4)
  )
```

The three models are reading pixels, not a vexillological gazetteer, so
shading, coats of arms, and gold-versus-yellow will produce disagreements.
The cache file at `r cache_path` can be re-used on the next knit.

The table below lists every flag where Gemini Lite, Qwen, and Gemini 3.6 Flash
do not all give the same count. Replace the `NA`s with a hand count.
Everyone else keeps Gemini Lite's number.

```{r flag-n-colours}
hand_counts <- tribble(
  ~country,              ~corrected_n,
  "Andorra",             5,               # Black was incorrectly detected
  "Belize",              8,               # Multiple colours in the crest
  "Burundi",             3,               # All models saw a gold colour that is not visible to the eye
  "Cambodia",            4,               # Gemini 3.6 Flash picked up the missing black outline colour
  "Croatia",             6,               # Flash picked up the missing black colour
  "Dominica",            7,               # Qwen was wrong
  "Dominican Republic",  6,               # Qwen was wrong although I can't say if it's brown/black
  "El Salvador",         6,               # Brown cannot be spotted and the flag has a rainbow
  "Equatorial Guinea",   8,               # Black and grey missed by all
  "Eswatini",            5,               # Flash lite saw an additional grey
  "Ethiopia",            4,               # Qwen failed to see blue
  "Fiji",                8,               # Black missed by all
  "Guatemala",           8,               # Flash got it correct, Lite missed red
  "Jordan",              4,               # Lite incorrectly saw a yellow
  "Kenya",               4,               # Lite incorrectly saw a grey
  "Liechtenstein",       4,               # Flash got it correct, the others missed the black outlines
  "Malta",               3,               # Qwen failed to spot grey
  "Mexico",              11,              # Qwen saw the coat of arms but did not include its colours in the count
  "Moldova",             6,               # Lite and Qwen saw a white that is not present
  "Mozambique",          5,               # Lite and Qwen saw a blue that is not present
  "Nicaragua",           6,               # Qwen failed to see brown and another flag that has a rainbow
  "Papua New Guinea",    4,               # Lite and Qwen failed to see white
  "Paraguay",            6,               # Lite and Qwen failed to see black
  "San Marino",          7,               # Qwen failed to see brown and yellow
  "Serbia",              6,               # Flash and Qwen failed missed the black outlines
  "Slovenia",            4,               # Qwen failed to spot the yellow
  "Spain",               7,               # Qwen failed to spot the green and purple
  "Turkmenistan",        4,               # Lite saw a black that is not present
  "Tuvalu",              5,               # Lite and Qwen failed to see white
  "Uruguay",             4,               # Lite and Qwen failed to see brown
  "Uzbekistan",          4,               # Lite saw a yellow that is not present
  "Zimbabwe",            5,               # Lite and Qwen saw a gold that is not present
)

results <- results |>
  left_join(hand_counts, by = "country") |>
  mutate(
    models_disagree = gemini_n_colours != judge_n_colours |
      gemini_n_colours != flash_n_colours |
      judge_n_colours != flash_n_colours,
    flag_n_colours = coalesce(corrected_n, gemini_n_colours)
  )

results |>
  filter(models_disagree) |>
  select(
    country,
    gemini_n_colours, judge_n_colours, flash_n_colours,
    corrected_n, flag_n_colours
  ) |>
  arrange(country)
```

```{r flag-n-colours-chart, fig.width=8, fig.height=5}
colour_counts <- results |>
  count(flag_n_colours, name = "flags")
three_colour_flags <- colour_counts$flags[colour_counts$flag_n_colours == 3]
three_colour_x <- match(3, sort(unique(colour_counts$flag_n_colours)))

colour_counts |>
  ggplot(aes(x = factor(flag_n_colours), y = flags)) +
    geom_col(width = 0.68) +
    geom_text(
      aes(label = flags),
      vjust = -0.45,
      size = 3.5
    ) +
    annotate(
      "text",
      x = three_colour_x + 1.15,
      y = three_colour_flags * 1.05,
      label = "3 colours are the most common",
      hjust = 0,
      size = 3.5
    ) +
    annotate(
      "curve",
      x = three_colour_x + 1.1,
      xend = three_colour_x + 0.4,
      y = three_colour_flags * 1.04,
      yend = three_colour_flags * 1.02,
      curvature = 0.3,
      arrow = grid::arrow(length = grid::unit(0.15, "inches")),
      linewidth = 0.5
    ) +
    scale_x_discrete(name = NULL) +
    scale_y_continuous(
      name = NULL,
      expand = expansion(mult = c(0, 0.18)),
      breaks = scales::pretty_breaks()
    ) +
    labs(
      title = "How many colours are in each national flag?",
      caption = stringr::str_wrap(
        "Hand-corrected counts where Gemini Lite, Qwen, and Gemini 3.6 Flash disagree; Gemini 3.5 Flash Lite otherwise. Sources: Wikipedia, Wikimedia Commons.",
        width = 95
      )
    ) +
    theme_gray() +
    theme(
      axis.ticks.y = element_blank(),
      axis.text.y = element_blank(),
      axis.title.x = element_text(margin = margin(t = 8)),
      plot.caption = element_text(size = 7),
      plot.margin = margin(10, 10, 14, 10)
    ) +
    coord_cartesian(clip = "off")
```
