---
title: "DAK sick-absence duration, 2025"
output: html_document
---

In German health-insurance statistics, **AU** is *Arbeitsunfähigkeit*: a
medically certified spell of being unfit for work. *AU-Fälle* are those
spells (absences); *AU-Tage* are the calendar days they cover.

The DAK *Gesundheitsreport 2026* (data year 2025) splits AU spells by
duration and reports each band's share of cases and of days (Figure 10).
This notebook redraws that as two 100% stacked bars — one for the mix of
absences, one for the mix of sick days — following Cole Nussbaumer
Knaflic's *Storytelling with Data* habits:

- Lead with a sentence title that states the finding.
- Use composition (stacked 100% bars) because the claim is about shares
  of a whole, not a ranking of six durations.
- Put the two categories that carry the story (1–3 days and 43+ days) in
  strong colour; push the rest into grey.
- Stack 1–3 days at the baseline so those slices are easy to compare
  across bars; put 43+ days at the far end.
- Label only the slices in focus.
- Strip chart junk.

Source: DAK-Gesundheit, *Gesundheitsreport 2026*, Figure 10.
Values sum to 100% in each bar.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.retina = 2)
```

```{r packages, message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r data}
duration_levels <- c(
  "1–3 days", "4–7 days", "8–14 days",
  "15–28 days", "29–42 days", "43+ days"
)

dak_duration <- tibble(
  duration = factor(duration_levels, levels = duration_levels),
  `Share of absences` = c(40.1, 33.0, 16.0, 6.3, 2.1, 2.5),
  `Share of sick days` = c(8.3, 16.9, 16.7, 12.6, 7.6, 37.9)
)

dak_long <- dak_duration %>%
  pivot_longer(
    cols = c(`Share of absences`, `Share of sick days`),
    names_to = "metric",
    values_to = "percent"
  ) %>%
  mutate(
    metric = factor(
      metric,
      levels = rev(c("Share of absences", "Share of sick days"))
    ),
    focus = duration %in% c("1–3 days", "43+ days")
  ) %>%
  group_by(metric) %>%
  arrange(duration, .by_group = TRUE) %>%
  mutate(
    xmax = cumsum(percent),
    xmin = xmax - percent,
    xmid = (xmin + xmax) / 2
  ) %>%
  ungroup()

dak_long
```

```{r chart, fig.width=8.6, fig.height=4.8, dpi=150}
palette <- c(
  "1–3 days" = "#2B6CB0",
  "4–7 days" = "#E4E4E4",
  "8–14 days" = "#D4D4D4",
  "15–28 days" = "#C4C4C4",
  "29–42 days" = "#B4B4B4",
  "43+ days" = "#C44E52"
)

# Draw with geom_rect so stack order matches the labelled midpoints.
# ggplot's position_stack can reverse fill order on horizontal bars.
metric_levels <- c("Share of sick days", "Share of absences")
dak_plot <- dak_long %>%
  mutate(
    y = as.numeric(factor(as.character(metric), levels = metric_levels)),
    ymin = y - 0.28,
    ymax = y + 0.28
  )

focus_labels <- dak_plot %>%
  filter(focus) %>%
  mutate(
    label = sprintf("%.1f%%", percent),
    label_x = if_else(percent < 6, xmax + 1.3, xmid),
    hjust = if_else(percent < 6, 0, 0.5),
    colour = if_else(percent < 6, "#C44E52", "white")
  )

p <- ggplot(dak_plot) +
  geom_rect(
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = duration),
    colour = "white",
    linewidth = 0.35
  ) +
  geom_text(
    data = focus_labels,
    aes(x = label_x, y = y, label = label, hjust = hjust, colour = colour),
    size = 3.4,
    fontface = "bold",
    family = "sans"
  ) +
  scale_colour_identity() +
  scale_fill_manual(
    values = palette,
    breaks = c("1–3 days", "43+ days"),
    name = NULL
  ) +
  scale_x_continuous(
    limits = c(0, 108),
    breaks = c(0, 25, 50, 75, 100),
    labels = function(x) paste0(x, "%"),
    expand = expansion(mult = c(0, 0.02))
  ) +
  scale_y_continuous(
    breaks = c(1, 2),
    labels = metric_levels
  ) +
  labs(
    title = "A few long absences do most of the work in the 19.5-day average",
    subtitle = "DAK-insured employees, 2025. Grey slices are absences of 4–42 days.",
    x = NULL,
    y = NULL,
    caption = "Source: DAK-Gesundheit, Gesundheitsreport 2026, Figure 10. Calendar days, including weekends."
  ) +
  theme_minimal(base_size = 12, base_family = "sans") +
  theme(
    plot.title = element_text(face = "bold", size = 13.5, colour = "#222222"),
    plot.subtitle = element_text(size = 10.5, colour = "#555555", margin = margin(b = 8)),
    plot.caption = element_text(size = 8.5, colour = "#777777", hjust = 0, margin = margin(t = 8)),
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(b = 4),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(colour = "#EEEEEE"),
    axis.text.y = element_text(colour = "#222222", size = 11, face = "bold"),
    axis.text.x = element_text(colour = "#666666"),
    plot.background = element_rect(fill = "white", colour = NA),
    panel.background = element_rect(fill = "white", colour = NA)
  )

p

out_path <- file.path("..", "static", "charts", "dak-absence-duration.png")
ggsave(out_path, p, width = 8.6, height = 4.6, dpi = 150, bg = "white")
```
